### 2021-01-19 paper/localpsf.tex
remove redundancy between mean cov theorem and algorithm

Since $\phi_x$ is nonnegative, it is a scaled probability distribution. Let $\alpha(x)$ denote the scaling factor, and let $\mu(x)$ and $\Sigma(x)$ denote the mean and covariance of the normalized version of $\phi_x$ (see Definition \ref{defn:alpha_rho_mu_sigma}). We make the approximation that the support of $\phi_x$ is contained within the ellipsoid
\begin{equation}
\label{eq:support_ellipsoid}
E_x := \{x' \in \Omega: (x' - \mu(x))^T \Sigma(x)^{-1} (x' - \mu(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. 
%The ellipsoid $E_{x}$ is the set of points within $\tau$ standard deviations of the mean of the Gaussian approximation of the normalized version of $\langle \mathcal{A}, \delta_{x}\rangle^{*}$ which has the same mean and covariance. 
The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\mu(x)$ and covariance $\Sigma(x)$, i.e., the Gaussian distribution which has the same mean and covariance as the normalized version of $\phi_x$ (see Figure FIG). The bigger $\tau$ is, the smaller the overlap between impulse responses within a batch will be, while the smaller $\tau$ is, the more impulse responses we can fit within each batch. In practice we find that $\tau=3$ provides a good balance between these competing goals. 
The fraction of the ``mass'' of $\phi_x$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though we find this bound is conservative and far less mass resides in this region in practice.

In Algorithm \ref{alg:varhpi_mean_cov} we show how to compute $\alpha(x)$, $\mu(x)$, and $\Sigma(x)$ for all points $x$ simultaneously, by applying $\mathcal{A}^T$ to a constant function and a small number of linear and quadratic functions. The theoretical basis for Algorithm \ref{alg:varhpi_mean_cov} is shown in Theorem \ref{thm:vol_mean_cov}.

@@

\begin{defn}
	\label{defn:alpha_rho_mu_sigma}
	We define the spatially scaling factor, $\alpha$, the scaled impulse response, $\rho_x$, the spatially varying mean, $\mu$, and the spatially varying covariance, $\Sigma$, as follows:
	\begin{align*}
	\alpha:\Omega \rightarrow \mathbb{R}, &\qquad \alpha(x) := \int_{\Omega} \phi_x(z) dz, \\
	\rho_x:\Omega \rightarrow \mathbb{R}, &\qquad \rho_x := \phi_x \big/ \alpha(x), \\
	\mu:\Omega \rightarrow \mathbb{R}^d, &\qquad \mu(x) := \int_\Omega z \rho_x(z) dz, \\
	\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}, &\qquad\Sigma(x) := \int_\Omega (z - \mu(x))(z - \mu(x))^T \rho_x(z) dz.
	\end{align*}
\end{defn}

\begin{theorem}
	\label{thm:vol_mean_cov}
	Let  $x^i$ denote the $i^\text{th}$ component of $x$, i.e., $x = \left(x^1, x^2, \dots, x^d\right)$, and let $C$, $\{L^i\}_{i=1}^d$, and ${\{Q^{ij}\}_{i=1}^d}_{j=1}^d$ be the following constant, linear, and quadratic functions, respectively:
	\begin{equation*}
		C(x) := 1, \qquad
		L^i(x) := x^i, \qquad
		Q^{ij}(x) = x^i x^j.
	\end{equation*}
	We have
	\begin{align}
		\alpha =& \left(\mathcal{A}^TC\right)^*, \label{eq:vol_mean_var_thm1}\\
		\mu^i =& \left(\mathcal{A}^T L^i\right)^* / \alpha, \label{eq:vol_mean_var_thm2}\\
		\Sigma^{ij} =& \left(\mathcal{A}^T Q^{ij}\right)^* / \alpha - \mu^i\cdot\mu^j, \label{eq:vol_mean_var_thm3}
	\end{align}
	We write $f/g$ to denote the pointwise division of functions, $\left(f/g\right)(x) = f(x)/g(x)$, and $f\cdot g$ to denote the pointwise multiplication of functions, $(f\cdot g)(x) = f(x)g(x)$.
\end{theorem}

@@

@@

\begin{proof}[Proof of Theorem \ref{thm:vol_mean_cov}]
	Let $w \in L^2$ be arbitrary. We have
	\begin{align*}
		\left(w, \alpha\right)_{L^2(\Omega)} =& \int_\Omega w(x) \int_{\Omega} \langle\mathcal{A},\delta_x\rangle^*(z) dz dx\\
		=& \int_\Omega w(x) \int_{\Omega} A(z,x) dz dx \\
		=& \int_\Omega \int_\Omega w(x) A(z,x) C(z) dz dx \\
		=& \left(\mathcal{A}^T C\right)(w),
	\end{align*}
	which implies \eqref{eq:vol_mean_var_thm1}.

	Using similar techniques, we have
	\begin{align*}
		\left(w, \alpha \cdot \mu^i\right)_{L^2(\Omega)} =& \int_\Omega w(x) \alpha(x) \int_{\Omega} z^i \langle\mathcal{A},\delta_x\rangle^*(z)/\alpha(x) dz dx\\
		=& \int_\Omega \int_\Omega w(x) L^i(z) A(z,x) dz dx \\
		=& \left(\mathcal{A}^T L^i\right)(w),
	\end{align*}
	which implies \eqref{eq:vol_mean_var_thm2}.

	To prove \eqref{eq:vol_mean_var_thm3} we use the identity
	\begin{equation*}
		\Sigma(x) = \int_\Omega zz^T \rho_x(z) dz - \mu(x) \mu(x)^T.
	\end{equation*}
	We have
	\begin{align*}
		\left(w, \alpha \cdot \left(\Sigma^{ij}+\mu^i \cdot \mu^j\right)\right)_{L^2(\Omega)} =& \int_\Omega w(x) \alpha(x) \int_\Omega z^i z^j \langle\mathcal{A},\delta_x\rangle^*(z) / \alpha(x) dz dx \\
		=& \int_\Omega \int_\Omega w(x) Q^{ij}(z) A(z,x) dz dx \\
		=& \left(\mathcal{A}Q^{ij}\right)(w),
	\end{align*}
	which implies \eqref{eq:vol_mean_var_thm3}.

>>>>

Since $\phi_x$ is nonnegative, it is a scaled probability distribution. Let $\widehat{\phi}_x$ denote the normalized version of $\phi_x$, and let $\mu(x)$ and $\Sigma(x)$ denote the mean and covariance of $\widehat{\phi}_x$, respectively (see Definition \ref{defn:alpha_rho_mu_sigma}). We make the approximation that the support of $\phi_x$ is contained within the ellipsoid
\begin{equation}
\label{eq:support_ellipsoid}
E_x := \{x' \in \Omega: (x' - \mu(x))^T \Sigma(x)^{-1} (x' - \mu(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. 
%The ellipsoid $E_{x}$ is the set of points within $\tau$ standard deviations of the mean of the Gaussian approximation of the normalized version of $\langle \mathcal{A}, \delta_{x}\rangle^{*}$ which has the same mean and covariance. 
The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\mu(x)$ and covariance $\Sigma(x)$, i.e., the Gaussian distribution which has the same mean and covariance as $\widehat{\phi}_x$ (see Figure FIG). The bigger $\tau$ is, the smaller the overlap between impulse responses within a batch will be, while the smaller $\tau$ is, the more impulse responses we can fit within each batch. In practice we find that $\tau=3$ provides a good balance between these competing goals. 
The fraction of the ``mass'' of $\phi_x$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though we find this bound is conservative and far less mass resides in this region in practice.

In Algorithm \ref{alg:varhpi_mean_cov} we show how to compute $\alpha(x)$, $\mu(x)$, and $\Sigma(x)$ for all points $x$ simultaneously, by applying $\mathcal{A}^T$ to a constant function and a small number of linear and quadratic functions. Definitions required for Algorithm \ref{alg:varhpi_mean_cov} are given in Definition \ref{defn:alpha_rho_mu_sigma}, Definition \ref{defn:C_L_Q}, and Definition \ref{defn:pointwise}. The theoretical basis for Algorithm \ref{alg:varhpi_mean_cov} is shown in Theorem \ref{thm:vol_mean_cov}.

@@

\begin{defn}[Moments of $\phi_x$]
	\label{defn:alpha_rho_mu_sigma}
	We define the spatially scaling factor, $\alpha$, the scaled impulse response, $\widehat{\phi}_x$, the spatially varying mean, $\mu$, and the spatially varying covariance, $\Sigma$, as follows:
	\begin{align*}
	\alpha:\Omega \rightarrow \mathbb{R}, &\qquad \alpha(x) := \int_{\Omega} \phi_x(z) dz, \\
	\widehat{\phi}_x:\Omega \rightarrow \mathbb{R}, &\qquad \widehat{\phi}_x := \phi_x \big/ \alpha(x), \\
	\mu:\Omega \rightarrow \mathbb{R}^d, &\qquad \mu(x) := \int_\Omega z \widehat{\phi}_x(z) dz, \\
	\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}, &\qquad\Sigma(x) := \int_\Omega (z - \mu(x))(z - \mu(x))^T \widehat{\phi}_x(z) dz.
	\end{align*}
\end{defn}

\begin{defn}[Constant, linear, and quadratic functions]	
	\label{defn:C_L_Q}
	Let  $x^i$ denote the $i^\text{th}$ component of $x$, i.e., $x = \left(x^1, x^2, \dots, x^d\right)$. We define $C$, $\{L^i\}_{i=1}^d$, and ${\{Q^{ij}\}_{i=1}^d}_{j=1}^d$ be the following constant, linear, and quadratic functions, respectively:
	\begin{equation*}
	C(x) := 1, \qquad
	L^i(x) := x^i, \qquad
	Q^{ij}(x) = x^i x^j.
	\end{equation*}
\end{defn}

\begin{defn}[Pointwise operations]
	\label{defn:pointwise}
	We write $f/g$ to denote the pointwise division of functions, $\left(f/g\right)(x) = f(x)/g(x)$, and $f\cdot g$ to denote the pointwise multiplication of functions, $(f\cdot g)(x) = f(x)g(x)$.
\end{defn}

%\begin{theorem}
%	\label{thm:vol_mean_cov}
%	Let  $x^i$ denote the $i^\text{th}$ component of $x$, i.e., $x = \left(x^1, x^2, \dots, x^d\right)$, and let $C$, $\{L^i\}_{i=1}^d$, and ${\{Q^{ij}\}_{i=1}^d}_{j=1}^d$ be the following constant, linear, and quadratic functions, respectively:
%	\begin{equation*}
%		C(x) := 1, \qquad
%		L^i(x) := x^i, \qquad
%		Q^{ij}(x) = x^i x^j.
%	\end{equation*}
%	We have
%	\begin{align}
%		\alpha =& \left(\mathcal{A}^TC\right)^*, \label{eq:vol_mean_var_thm1}\\
%		\mu^i =& \left(\mathcal{A}^T L^i\right)^* / \alpha, \label{eq:vol_mean_var_thm2}\\
%		\Sigma^{ij} =& \left(\mathcal{A}^T Q^{ij}\right)^* / \alpha - \mu^i\cdot\mu^j, \label{eq:vol_mean_var_thm3}
%	\end{align}
%	We write $f/g$ to denote the pointwise division of functions, $\left(f/g\right)(x) = f(x)/g(x)$, and $f\cdot g$ to denote the pointwise multiplication of functions, $(f\cdot g)(x) = f(x)g(x)$.
%\end{theorem}
%
%The proof of Theorem \ref{thm:vol_mean_cov} is shown in Appendix \ref{app:proofs}.

@@

\begin{theorem}[Correctness of Algorithm \ref{alg:varhpi_mean_cov}]
	\label{thm:vol_mean_cov}
	Algorithm \ref{alg:varhpi_mean_cov} correctly computes $\alpha$, $\mu$, and $\Sigma$.
\end{theorem}

@@

\begin{proof}[Proof of Theorem \ref{thm:vol_mean_cov}]
	Let $w \in L^2$ be arbitrary. We have
	\begin{align*}
		\left(w, \alpha\right)_{L^2(\Omega)} =& \int_\Omega w(x) \int_{\Omega} \langle\mathcal{A},\delta_x\rangle^*(z) dz dx\\
		=& \int_\Omega w(x) \int_{\Omega} A(z,x) dz dx \\
		=& \int_\Omega \int_\Omega w(x) A(z,x) C(z) dz dx \\
		=& \left(\mathcal{A}^T C\right)(w),
	\end{align*}
	which implies $\alpha = \left(\mathcal{A}^TC\right)^*$.

	Using similar techniques, we have
	\begin{align*}
		\left(w, \alpha \cdot \mu^i\right)_{L^2(\Omega)} =& \int_\Omega w(x) \alpha(x) \int_{\Omega} z^i \langle\mathcal{A},\delta_x\rangle^*(z)/\alpha(x) dz dx\\
		=& \int_\Omega \int_\Omega w(x) L^i(z) A(z,x) dz dx \\
		=& \left(\mathcal{A}^T L^i\right)(w),
	\end{align*}
	which implies $\mu^i = \left(\mathcal{A}^T L^i\right)^* / \alpha$.

	Using the identity
	\begin{equation*}
		\Sigma(x) = \int_\Omega zz^T \widehat{\phi}_x(z) dz - \mu(x) \mu(x)^T,
	\end{equation*}
	we have
	\begin{align*}
		\left(w, \alpha \cdot \left(\Sigma^{ij}+\mu^i \cdot \mu^j\right)\right)_{L^2(\Omega)} =& \int_\Omega w(x) \alpha(x) \int_\Omega z^i z^j \langle\mathcal{A},\delta_x\rangle^*(z) / \alpha(x) dz dx \\
		=& \int_\Omega \int_\Omega w(x) Q^{ij}(z) A(z,x) dz dx \\
		=& \left(\mathcal{A}Q^{ij}\right)(w),
	\end{align*}
	which implies $\Sigma^{ij} = \left(\mathcal{A}^T Q^{ij}\right)^* / \alpha - \mu^i\cdot\mu^j$.
